---
title: "Shifting / Enlarging"
author: "Subin / Connor"
date: "2023-10-27"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


used this tool to install packages that were not available on CRAN - installed from GitHub Repository
```{r}
devtools::install_github("UrbanInstitute/urbnmapr")
```

adding Palau to territories_state data frame 
1. loading shapefiles
```{r}

```
2. creating multipolygon from a single polygon 
```{r}
shifted_enlarged_polygon <- st_sfc(
  st_polygon(list(
    rbind(
      c(134.5825 + 2, 7.5150 + 3),   # Shifted and enlarged coordinates
      c(134.5825 + 3, 7.5150 + 4),   # Adjust the shift and enlargement factors as needed
      c(134.5825 + 4, 7.5150 + 4),
      c(134.5825 + 4, 7.5150 + 3),
      c(134.5825 + 2, 7.5150 + 3)
    )
  ))
)

# Print the multipolygon in WKT format
cat(st_as_text(shifted_enlarged_polygon))
```
3. now create an sf object palau sf from the WKT representation of the polygon 
```{r}
# WKT format representation of the polygon
wkt_palau <- "MULTIPOLYGON (((136.5825 10.5150, 137.5825 11.5150, 137.5825 12.5150, 136.5825 12.5150, 136.5825 10.5150)))"

# Convert to an sf object
palau_sf <- st_as_sf(data.frame(id = 1, wkt = wkt_palau), wkt = "wkt")
```
4. now bind the row to add palau to territories_state 
```{r}
combined_data <- bind_rows(territories_states, palau_sf)
```
5. succesfully binded in combined_data but need to fix rows - remove wkt and id and add Palau data in wkt column to geometry 
```{r}
territories_states <- get_urbn_map(map = "territories_states", sf = TRUE)
#WKT format representation of the polygon for Palau
wkt_palau <- "MULTIPOLYGON (((136.5825 10.5150, 137.5825 11.5150, 137.5825 12.5150, 136.5825 12.5150, 136.5825 10.5150)))"

# Convert WKT to an sf object
palau_sf <- st_as_sf(data.frame(wkt = wkt_palau), wkt = "wkt")

# Combine "palau_sf" with "territories_states" and update the geometry
combined_data <- bind_rows(territories_states, palau_sf) %>%
  st_set_geometry(st_geometry(palau_sf))

# Drop the "wkt" column
combined_data <- combined_data %>%
  select(-wkt)

# Print the combined dataset
print(combined_data)

```

^ didn't really work out, lets try Marshall Islands and FSM 
```{r}
#coordinates 
marshall_islands_coords <- c(171.1845, 7.1315)
fsm_coords <- c(150.5508, 7.4256)

#create sf objects 
marshall_islands_sf <- st_point(c(marshall_islands_coords))
fsm_sf <- st_point(c(fsm_coords))

#shift/enlargement factors (might need to adjust later)
shift_factor <- c(2, 2)  # Shift by 2 degrees in both directions
enlarge_factor <- 1.5    # Enlarge by 1.5 times

#apply those to the geometries 
marshall_islands_sf <- st_transform(st_translate(st_scale(marshall_islands_sf, scale = enlarge_factor), shift = shift_factor), crs = st_crs(territories_states))
fsm_sf <- st_transform(st_translate(st_scale(fsm_sf, scale = enlarge_factor), shift = shift_factor), crs = st_crs(territories_states))

#combine to territories_state data set
combined_data <- bind_rows(territories_states, marshall_islands_sf, fsm_sf)

#new: drop the unwanted columns 
combined_data <- combined_data %>%
  select(-wkt)  

#print combined data set
print(combined_data)
```

trying to access territories_state full geometry version 
```{r}
full_geometry <-territories_states$geometry

full_geometry_wkt <- sf::st_as_text(territories_states$geometry)

cat(full_geometry_wkt)

```

restarting, deleted all files 
```{r}
rm(geo_sf)
```

```{r}
# Load necessary library
library(jsonlite)

# Your JSON string
json_string <- '[
  {"type":"Feature","geometry":{"type":"MultiPolygon","coordinates":[[[[163.01,5.26],[162.9,5.31],[163.02,5.38],[163.01,5.26]]],[[[158.3,6.79],[158.12,6.93],[158.32,6.93],[158.3,6.79]]],[[[138.21,9.52],[138.06,9.42],[138.13,9.57],[138.21,9.52]]]]},"properties":{"name":"Micronesia, Federated States of"},"id":"FM"},
  {"type":"Feature","geometry":{"type":"MultiPolygon","coordinates":[[[[168.77,7.3],[168.79,7.29],[168.67,7.33],[168.77,7.30]]],[[[168.57,7.40],[168.55,7.42],[168.56,7.47],[168.57,7.40]]],[[[168.97,7.57],[168.94,7.62],[168.97,7.60],[168.97,7.57]]]]},"properties":{"name":"Marshall Islands"},"id":"MH"},
  {"type":"Feature","geometry":{"type":"MultiPolygon","coordinates":[[[[134.56,7.37],[134.49,7.44],[134.63,7.73],[134.56,7.37]]]]},"properties":{"name":"Palau"},"id":"PW"}
]'

# Convert JSON string to data frame
geo_data <- fromJSON(json_string)

# View the structure of the imported data frame
str(geo_data)

```
shift and enlarge the 3 islands by a factor of 3 
```{r}
# Load necessary libraries
library(sf)

# Example shift values
dx <- 3
dy <- 3
scale_factor <- 3

# Iterate through the rows of geo_data and create sf objects
sf_objects <- lapply(geo_data$geometry$coordinates, function(coords) {
  # Convert the coordinates to matrix and check if the polygon is closed
  coords_matrix <- matrix(coords, ncol = 2, byrow = TRUE)
  if (!identical(coords_matrix[1, ], coords_matrix[nrow(coords_matrix), ])) {
    coords_matrix <- rbind(coords_matrix, coords_matrix[1, ])
  }
  
  # Shift and scale the coordinates manually
  coords_matrix <- coords_matrix * scale_factor + c(dx, dy) * (scale_factor - 1)
  
  # Create an sf polygon
  st_polygon(list(coords_matrix))
})

# Create an sf multipolygon
enlarged_geo_sf <- st_sfc(sf_objects)

# View the resulting sf object
print(enlarged_geo_sf)

```
covert enlarged_geo_sf to a data frame 
```{r}
enlarged_df <- as.data.frame(enlarged_geo_sf)
```